# Results

## Case Study: USSR

Let us first look at the history of the USSR.

```{r}
# Timeline taken from:
# https://en.wikipedia.org/wiki/List_of_leaders_of_the_Soviet_Union
library(vistime)
library(highcharter)
ussr_history <- data.frame(event = c("Lenin", "Stalin", "Malenkov", 
                                     "Khruschev", "Brezhnev", "Andropov", 
                                     "Chernenko", "Gorbachev", "End of USSR"), 
                            start = c("1922-12-30", "1924-01-21", "1953-03-05", "1953-09-14", "1964-10-14", "1982-11-10", "1984-02-09", "1985-03-10", "1991-12-25"), 
                            end = c("1924-01-21", "1953-03-05", "1953-09-14", "1964-10-14", "1982-11-10", "1984-02-09", "1985-03-10", "1991-12-25", "2000-01-01"), 
                            group = "Leaders of USSR")

hc_vistime(ussr_history)
```

From here we can see 4 major leaders of USSR: Stalin, Khruschev, Brezhnev and Gorbachev. The leaders in between - Malenkov, Andropov and Chernenko, are leaders in transition periods, as seen by the short tenure of each of them. We can expect to see some tumultuous activity both inside, by the motion of the elites as well as from the outside world. First, let's see the statistics of the elites that had their careers cut short during each of these periods.


```{r}
library(ggplot2) 
library(dplyr)
# Data
ussr <- read.csv("data/ARED/USSR_cleaned.csv")
china <- read.csv("data/ARED/China_cleaned.csv")

ussr_grouped <- as.data.frame(ussr) %>%
  count(ELITE_EXITLEADER, ELITE_EXITTYPE)
ussr_grouped$ELITE_EXITLEADER[ussr_grouped$ELITE_EXITLEADER == ""] <- "End of USSR"

ggplot(ussr_grouped, aes(x = ELITE_EXITTYPE, y = n, fill = ELITE_EXITTYPE)) +
  geom_bar(position = "dodge", stat = "identity") +
  geom_text(aes(label = n), position = position_dodge(width = 0.9), 
            vjust = -0.4, color = "grey68") +
  facet_wrap(~ELITE_EXITLEADER) +
  # formatting
  ggtitle("Exit strategies",
          subtitle = "Popular ways to 'exit' an authoritarian regime based on leaders") +
  labs(x = "Ways to 'exit' an authoritarian regime", y = "# of elites 'exiting' this way", 
       caption = "Source: ARED USSR database") +
  theme(plot.title = element_text(face = "bold")) +
  theme(axis.ticks.x = element_blank()) +
  theme(axis.text.x = element_blank()) +
  theme(plot.subtitle = element_text(face = "bold", color = "grey35")) +
  theme(plot.caption = element_text(color = "grey68"))
```

From this graph, we can see that the shorter the regime is (Andropov, Chernenko) the less drastic the changes. One outlier here is Malenkov, where there were many demotions despite the short time in power. This seems to align with the fact that he was a successor of Stalin, and was struggling to keep his power in Kremlin. That might also explain his short time in power.

Another observation is that Stalin was the most active in executing/exiling the elites, as he has the most death/expulsion counts among all of the leaders. This seems to coincide with history.

Finally, we can see that Gorbachev comes top in the number of resignations during his period. This may have to do with the fact that his regime was the last of USSR. It may be that many elites foresaw this downward tendency of the USSR and as such decided to resign before facing a dawning regime change.

```{r}
# bar chart showing timeline per leader in China/USSR
# Stability of tenure
ussr$ELITE_EXITLEADER[ussr$ELITE_EXITLEADER == ""] <- "End of USSR"
# boxplot by feed supplement 
ggplot(ussr, aes(x = reorder(ELITE_EXITLEADER, -ELITE_RETENURE, median), y = ELITE_RETENURE)) + 
  # plotting
  geom_boxplot(fill = "#bc7ddf", color = "#473e2c", position=position_dodge(1)) + 
  # formatting
  ggtitle("Not an Easy Job",
          subtitle = "Tenure of Authoritarian Elites During Different Leaders") +
  labs(x = "Leader", y = "Tenure in Years", caption = "Source: ARED USSR database") +
  theme(plot.title = element_text(face = "bold")) +
  theme(plot.subtitle = element_text(face = "bold", color = "grey35")) +
  theme(plot.caption = element_text(color = "grey68")) +
  scale_x_discrete(guide = guide_axis(n.dodge=3))
```

This is a boxplot showing the distribution of tenures during each leaders. Shorter tenures in light of group management can also mean instability. With the exception of Lenin (since his rule in USSR was so short), we can see that both
Malenkov and the End of USSR was a very tumultuous time, with median tenure being as low as 1~2 years. In contrast, we see that during times where there are less people leaving - Andropov, Brezhnev, Chernenko - we see that the average tenure was very long, and the people who left had been in power for a long time. This might show a time of generational change. For Brezhnev, we see a wide distribution as well as a large median tenure, as his regime lasted longer and was more stable. Despite a long time in power, it looks like the elites during Stalin and Khruschev were not able to stay too long, as they were frequently targets of demotion or expulsion based on the leaders' whim.

```{r}
academic <- c("Academic", "Academic director", "Academic lecturer", "Agricultural scientist", "Agronomist", "Economist", "Journalist", 
              "Teacher", "University Lecturer", "Historian")
engineering <- c("Chemical engineer", "Construction engineer", "Electrical engineer", "Electrician", "Factory engineer",
                 "Mechanican engineer", "Mechanic", "Metallurgical engineer", "Metalurgist", "Mining engineer", "Shipbuilding engineer",
                 "Technical engineer", "Machinist")
administrative <- c("Diplomat", "Lawyer", "Laywer", "Economic administrator", "Civil administrator", "Prosecutor", "Union organizer", "Trade unionist")
party <- c("Party functionary")
soldier <- c("Soldier", "State security")
worker <- c("Academic", "Engineer", "Administrative", "Party", "Soldier")
ussr_occ <- ussr
ussr_occ[ussr_occ$ELITE_OCCUPATION %in% academic, "ELITE_OCCUPATION"] <- "Academic"
ussr_occ[ussr_occ$ELITE_OCCUPATION %in% engineering, "ELITE_OCCUPATION"] <- "Engineer"
ussr_occ[ussr_occ$ELITE_OCCUPATION %in% administrative, "ELITE_OCCUPATION"] <- "Administrative"
ussr_occ[ussr_occ$ELITE_OCCUPATION %in% party, "ELITE_OCCUPATION"] <- "Party"
ussr_occ[ussr_occ$ELITE_OCCUPATION %in% soldier, "ELITE_OCCUPATION"] <- "Soldier"
`%notin%` <- Negate(`%in%`)
ussr_occ[ussr_occ$ELITE_OCCUPATION %notin% worker, "ELITE_OCCUPATION"] <- "Worker"
ussr_occ <- as.data.frame(ussr_occ) %>%
  count(ELITE_EXITLEADER, ELITE_OCCUPATION)
ggplot(ussr_occ, aes(fill=ELITE_OCCUPATION, y=n, x=ELITE_EXITLEADER)) + 
    ggtitle("Not My Dream Job",
          subtitle = "Previous Jobs of Elites Leaving During Leaders") +
  labs(x = "Leader", y = "Number of people in occupation", caption = "Source: ARED USSR database") +
  theme(plot.title = element_text(face = "bold")) +
  theme(plot.subtitle = element_text(face = "bold", color = "grey35")) +
  theme(plot.caption = element_text(color = "grey68")) +
    geom_bar(position="stack", stat="identity")+
  scale_x_discrete(guide = guide_axis(n.dodge=3))
```

One more thing that we can check is the makeup of the people who leave during the regimes. In a turbulent period where fights between
party members are frequent, we would see more party members leaving. It looks like Brezhnev and Stalin both had a lot of party members leaving the regime, hinting internal party quarrels. Also, it looks like soldiers were least likely to leave, which coincides with the powers that many soldiers had during the USSR. Finally, the number of members with administrative backgrounds leaving seems to correlate well with the overall number of elites leaving. The more people of administrative background leave, the more likely that there are elites leaving overall. This makes sense since these adminstrative roles would have played a large part in shaping policies, and a general downsizing/decline of the regime would affect these positions.